### 2018-05-03 2_wmm.tex
a bit of X.

@@

%"The semantics of a program is a set of executions" https://johnwickerson.github.io/papers/memalloy.pdf
The classical approach for modeling concurrent programs is to use the \textit{global time}, a single order of interleavings among all events happened in different threads.
Although these models are easy to understand, it may be impossible to process \textit{all} possible states, number of which is exponentially large.
However, there exist equivalence classes such that the result of execution different interleavings from single equivalence class is the same (for instance, computations performed by a processor locally do not affect the global state).
%One way to do this is to use a non-deterministic computation-centric model~\cite{fri97}, such as ...%The idea in this class of models is based on the fact that the behaviour of a concurrent system is defined only by the interleavings of shared-memory operations, while being independent from the order of local computation events.
%TODO: nondeterministic
One such model is the \textit{event-based} representation of a program, which models a program as a directed graph of events (the \textit{event-flow graph}).
The vertices of such a graph represent \textit{events} (independent low-level instructions; see Section~\ref{ch:wmm:model:events}), and edges represent \textit{relations} over the events (see Section~\ref{ch:wmm:model:relations}).

@@

A \textit{memory event} $e_m \in \mathbb{E}$ represents the fact of access to the memory. Since memory is the crucial low-level resource shared by multiple processes, most relations are defined over memory events. 
The processes can access a shared memory location (denoted by~$l_i$, for \textit{location}), or a local one (denoted by~$r_i$, for \textit{register}).
A memory event can access at most one shared memory location, high-level instructions that address more than one shared variable must be transformed into a sequence of events.
A memory event is specified by its direction with respect to the shared variable, its location~$\mathtt{loc}(e_m)$, its processor label~$\mathtt{proc}(e_m)$, and a unique event label~$\mathtt{id}(e_m)$~\cite{alglave2010shared}.
%\texttt{load} for read the value of a shared-memory location, or \texttt{store} for write, or neither of them if both locations are local

>>>>

%TODO: move this chapter as a section to introduction and add here the new "Problem statement" chapter!!!

@@

%"The semantics of a program is a set of executions" https://johnwickerson.github.io/papers/memalloy.pdf
The classical approach for modeling concurrent programs is to use the \textit{global time}, a single order of interleavings among all events happened in different threads.
Although these models are easy to understand, it may be impossible to treat \textit{all} possible states, number of which is exponentially large.
However, there exist equivalence classes such that the result of execution different interleavings from single equivalence class is the same (for instance, computations performed by a processor locally do not affect the global state).
%One way to do this is to use a non-deterministic computation-centric model~\cite{fri97}, such as ...%The idea in this class of models is based on the fact that the behaviour of a concurrent system is defined only by the interleavings of shared-memory operations, while being independent from the order of local computation events.
%TODO: nondeterministic
One such model is the \textit{event-based} representation of a program, which models a program as a directed graph of events (the \textit{event-flow graph}).
The vertices of such a graph represent \textit{events} (see Section~\ref{ch:wmm:model:events}), and edges represent \textit{basic relations} (see Section~\ref{ch:wmm:model:relations}).

@@

The event is an independent low-level atomic operation.

A \textit{memory event} $e_m \in \mathbb{E}$ represents the fact of access to the memory.
Only memory events change the state of an abstract machine executing the code, since it is completely determined by values stored in its memory.
Since memory is the crucial low-level resource shared by multiple processes, most relations are defined over memory events. 
The processes can access a shared memory location (denoted by~$l_i$, for \textit{location}), or a local one (denoted by~$r_i$, for \textit{register}).
A memory event can access at most one shared memory location, high-level instructions that address more than one shared variable must be transformed into a sequence of events.
A memory event is specified by its direction with respect to the shared variable, its location~$\mathtt{loc}(e_m)$, its processor label~$\mathtt{proc}(e_m)$, and a unique event label~$\mathtt{id}(e_m)$~\cite{alglave2010shared}.
%\texttt{load} for read the value of a shared-memory location, or \texttt{store} for write, or neither of them if both locations are local

### 2018-05-03 4_impl.tex
a bit of X.

\begin{figure}%[H]
    \centering
  %draft=true
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{img/my/draw.io/general_arch.png}
  \caption{The general architecture of \porthos[2]}
  \label{fig:arch}
\end{figure}

The program takes as input the program to be analysed and one (the reachability analysis mode) or two (the portability analysis mode) memory models. The parsed program syntax tree is then converted (Section~\ref{ch:impl:proc:y-constr}) to a program AST called \ytree{}%
\footnote{In order to avoid confusion between different internal representations, we prefix the names of elements of each internal representation with a letter. For instance, we picked the letter `Y' to denote the AST code representation as drawing of this letter resembles the tree branching; with letter `X' we prefix elements of the event-flow graph as the events are to be e\textbf{x}ecuted; and with letter `W' we prefix elements of the \textbf{w}eak memory model AST.} %
(Section~\ref{ch:impl:model:ytree})
%, and the memory model is being parsed (Section~\ref{ch:impl:proc:w-parser}) to another AST called \wmodel{} (Section~\ref{ch:impl:model:wmodel}).
, which then is being pre-processed at the pre-compilation stage (Section~\ref{ch:impl:proc:x-pre-compiler}) in order to collect information necessary for the compilation.
The \ytree{} then is being compiled (Section~\ref{ch:impl:proc:x-compiler}) to an \xgraph{} representation (Section~\ref{ch:impl:model:xgraph}).
The compiled \xgraph{} then undergoes a number of transformations (Section~\ref{ch:impl:proc:x-unroll}) necessary for the encoding into a \zformula{} (Section~\ref{ch:impl:model:zformula}) at the pre-encoding stage (Section~\ref{ch:impl:proc:x-unroll}).
Then, the memory-model constructor (Section~\ref{ch:impl:proc:w-constr}) constructs the derived relations on the basis of the \xgraph{} in order to build the weak memory model \wmodel{} (Section~\ref{ch:impl:model:wmodel}).
Thereafter, \wmodel{} and transformed \xgraph{} are encoded (Section~\ref{ch:impl:proc:z-encoder}) to a \zformula{} representation (a wrapper over an SMT logical formula), which then is passed as an input to the SMT-solver.

@@

  \item \texttt{YVariableRef} that stores the "reference" to a variable (viz., the name of an object);

@@

\begin{figure}[t]%[!b]%[H]
  \centering
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/class-diagrams/XEntity-interfaces.png}
  \caption{The inheritance tree of main interfaces of \xgraph{} elements}
  \label{fig:class-diagrams:XEntity-interfaces}
\end{figure}

@@

Following the terminology of the C standard, we distinguish the \textit{r-value} and \textit{l-value} memory units (l-values may be assigned the new value).
As r-values cannot change their value, they can be seen as the value itself (therefore the \texttt{XComputationEvent} is modelled as an local r-value memory unit, more detailed discussion goes further in current Section).

@@

@@

atomic action
XEventInfo

%comp event emulated by both -- optimisation?
Note, the computation-event \texttt{XComputationEvent} implements both \texttt{XEvent} and \texttt{XMemoryUnit}.
This is a model-level optimisation possible because a computation-event
%\textit{is} an event (thus it can form a node in \xgraph{}) and it also 
performs a computation over local-only memory and does not change the value of any memory unit, therefore the \textit{computation} abstraction (the CPU time) can be safely removed from the model, and the computation event can be seen as an atomic operation.

secondly, relations edges (special class? no, just map with enum as kind of edge)

CF edge: then-edge (primary), else-edge (alternative)

DF edge: co, rf

Kinds of events: (paragraph) <pciture>

memory events

computation: reduce to method call event
MethCallE (descr in transformer section)

XBarrierEvent - kinds

controlflow/ %TODO: rename package controlflow->empty (NOT FORGET TO UPDATE FILE TREE LISTING)
XNopEvent
XJumpEvent - no kinds, same as nop
entry
two kinds of exit

Valid graph: (paragraph)
- single source, two sinks
- connected
- each node has 1 or 2 children
- branching node (2 children) instanceof XComputationEvent (evaluation of the value, no shared-memory operations)
-

//Picture of the CF-graph
Consider the following code in C:

\subsubsection{W-model}
\label{ch:impl:model:wmodel}

a simple set of recursively defined relations

@@

@@

@@

same as y-tree constructor

@@

The ANTLR syntax tree of C

%, comparing to ANTLR syntax tree, does not have 
- desugar, equiv transform
- variables distinguished from

@@

- So, The language-dependent syntax tree is converted to the AST by the stateless Visitor (e.g., for C11->Ytree conversion is made by 'C2YtreeConverterVisitor') + short structure of this visitor (how?.. need ly?)

@@

@@

@@

%\textit{Type analysis} is the process of \textit{converting} the text-based type labels (obtained at variable declarations) to the type instances (modelled by the class \texttt{mousquetaires.languages.common.Type}) and \textit{propagating} them to all expressions.
%TODO: remake this paragraph considering that we have already said sth about XType
The C language has a static (resolved at compile-time) manifest (all types are declared explicitly) type system.
Comparing to languages that use type inference, the type analysis of a C program constitutes a simple propagating the type information (obtained from variables declarations) to all expressions.
%In \porthos[2], the type is modelled by the class \texttt{XType}.%TODO: + fix class and package name!
Being carried at Y and X representation levels, the type is converted to a Z-type at the Z-formula encoding stage (see Section~\ref{ch:impl:proc:z-encoder}).

@@

- X-Y-type construction: code of class YType2TypeConverter (todo: rename: it's not conversion, it's a type construction, from the y-level name+qualifiers+

- The typification algorithm: propagation rules for each of Y and X

- more about type abstraction: common for all levels. Simple label?

- data-model?

\paragraph{Invocation hooking.}
\label{ch:impl:proc:x-pre-compiler:hooks}

resolve the semantics of a function given its signature (arguments are already typed)

knowledge base

@@

no contexts yet

MethCallE : bind parameters with values (load them to temp registers) + remember the return-register
reutrn event= assign the return-register + simple jump

@@

how we attempted, why it didn't work in general case:
-

@@

@@

@@

Z-type : SMT-specific

@@

\subsubsection{}
\label{ch:impl:aux:watchdog}

- picture of the Y-hierarchy. everything inherits interface YEntity

- immutable

- AST is untyped (YVariableRef).

- short characteristics with citations from the code (this AST contains very basic language elements according to the C execution model (statements and expressions) )

- minor changes are performed by converting to ytree representation: desugaring the target code, etc. (what else?)

%\section{Model parser}
%\label{ch:impl:model}

TODO

\begin{figure}%[!b]%[H]
  \centering
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{img/my/class-diagrams/XEntity.png}
  \caption{TODO}
  \label{fig:class-diagrams:XEntity}
\end{figure}

\lstinputlisting{inc/XEventVisitor-cleaned.java}

@@

- interface that it provides

- dependencies on other modules (memory-manager, etc.)

\subsection{Pre-compilation}
\label{ch:impl:y2x:precomp}

- collect goto labels (not done yet.)

- determine kind of variables (cannot be done during parsing? don't say this)

%todo: after all, list which modules (classes, managers) are being initialised during the pre-compilation. I'ts good to have the dependencies graph on moduls (operational semantics:) )

%\subsection{Compilation}
%\label{ch:impl:y2x:compil}

- more low-level code representation (or high-level assembly); abstract assembly language. refer to the %2_wmm.tex

- X-hierarchie

%\subsection{Post-compilation}
%\label{ch:impl:x2y:postcomp}

transformations

- converting to SSA form (now: during the encoding. should be: during the post-compilation) (as one of necessary steps before encoding)

- setting up backward edges

- more?

The original program encoded into the \texttt{XGraph} represents a \textit{flow graph}, a connected cyclic directed graph with single source node \texttt{(ENTRY)} (usually for convenience all leaves are connected to the sink node \texttt{(EXIT)}). The cycles are caused by low-level jump instructions, obtained from non-linear high-level control-flow statements (such as \texttt{while}, \texttt{do-while}, \texttt{for}, etc.). However, the cyclic flow graph cannot be encoded into SMT formula since ...
//TODO:REFERENCE.%TODO

\begin{figure}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.5cm,semithick]
\node[c] (1) [] {$1$};
\node[c] (2) [below left of=1] {$2$};
\node[c] (3) [below right of=1] {$3$};
\node[c] (4) [below of=3] {$4$};
\path[->]
(1) edge [] node {} (2)
(2) edge [bend left=50,dotted] node {} (1)
(1) edge [] node {} (3)
(3) edge [] node {} (4)
(4) edge [bend right=80,dotted] node {} (1)
;
\node[draw=none] (impl) [right=3cm of 3] {$\overset{k = 6}{\longmapsto}$};
;
\node[c] (21) [right=3cm of impl] {$2_1$};
\node[c] (11) [above right=1cm and 1cm of 21]{$1_1$};
\node[c] (31) [below right=1cm and 1cm of 11] {$3_1$};
\node[c] (41) [below of=31] {$4_1$};
\node[c] (12) [below of=21] {$1_2$};
\node[c] (22) [below left=1cm and 1cm of 12] {$2_2$};
\node[c] (32) [below right=1cm and 1cm of 12] {$3_2$};
\node[c] (13) [below of=41] {$1_3$};
\node[c] (14) [below of=22] {$1_4$};
\node[c] (43) [below of=32] {$4_3$};
\node[c] (23) [below of=13] {$2_3$};
\node[c] (33) [below of=13] {$3_3$};
\node[c] (24) [below left=1cm and 1cm of 14] {$2_4$};
\node[c] (34) [below right=1cm and 1cm of 14] {$3_4$};
\node[c] (15) [below right=1cm and -0.3cm of 43] {$1_5$};
\node[c] (44) [below of=33] {$4_4$};
\node[c] (6) [below left=1cm and 1cm of 15] {$6$};
\node[] (11k) [right=3.2cm of 11] {$(k = 1)$};
\node[] (31k) [right=1.7cm of 31] {$(k = 2)$};
\node[] (41k) [right=1.7cm of 41] {$(k = 3)$};
\node[] (13k) [right=1.7cm of 13] {$(k = 4)$};
\node[] (33k) [right=1.7cm of 33] {$(k = 5)$};
\node[] (44k) [right=1.7cm of 44] {$(k = 6)$};
\path[->]
(11) edge [] node {} (21)
(11) edge [] node {} (31)
(31) edge [] node {} (41)
(21) edge [] node {} (12)
(12) edge [bend right=10] node {} (22)
(12) edge [bend left=10] node {} (32)
(41) edge [] node {} (13)
(22) edge [] node {} (14)
(32) edge [] node {} (43)
(13) edge [] node {} (23)
(13) edge [] node {} (33)
(14) edge [bend right=10] node {} (24)
(14) edge [bend left=10] node {} (34)
(43) edge [] node {} (15)
(33) edge [bend right=10] node {} (15)
(33) edge [bend left=10] node {} (44)
(24) edge [bend right=20] node {} (6)
(34) edge [] node {} (6)
(15) edge [] node {} (6)
(44) edge [bend left=20] node {} (6)
;
\end{tikzpicture}
\label{fig:loop-unwind}
\caption{Example of the flow graph from Figure~\ref{fig:merged-loop.....}, unwinded up to the bound $k = 6$}
\end{figure}

%\section{XGraph to ZFormula (SMT) encoder}
%\label{ch:impl:comp:zformula}

- Then, this modified event-representation is being encoded to SMT formula and sent to the solver.

% say something about equals() and hashCode()

>>>>

\begin{figure}%[H]
    \centering
  %draft=true
  \includegraphics[height=.99\textheight,keepaspectratio]{img/my/draw.io/general_arch.png}
  \caption{The general architecture of \porthos[2]}
  \label{fig:arch}
\end{figure}

The program takes as input the program to be analysed and one (the reachability analysis mode) or two (the portability analysis mode) memory models. The parsed program syntax tree is then converted (Section~\ref{ch:impl:proc:y-constr}) to a program AST called \ytree{}%
\footnote{In order to avoid confusion between different internal representations, we prefix the names of elements of each internal representation with a letter. For instance, we picked the letter `Y' to denote the AST code representation as drawing of this letter resembles the tree branching; with letter `X' we prefix elements of the event-flow graph as the events are to be e\textbf{x}ecuted; and with letter `W' we prefix elements of the \textbf{w}eak memory model AST.}%
(Section~\ref{ch:impl:model:ytree}), which then is being pre-processed at the pre-compilation stage (Section~\ref{ch:impl:proc:x-pre-compiler}) in order to collect information necessary for the compilation.
The \ytree{} then is being compiled (Section~\ref{ch:impl:proc:x-compiler}) to an \xgraph{} representation (Section~\ref{ch:impl:model:xgraph}).
The compiled \xgraph{} then undergoes a number of transformations (Section~\ref{ch:impl:proc:x-unroll}) necessary for the encoding into a \zformula{} (Section~\ref{ch:impl:model:zformula}) at the pre-encoding stage (Section~\ref{ch:impl:proc:x-unroll}).
Then, the memory-model constructor (Section~\ref{ch:impl:proc:w-constr}) constructs the derived relations on the basis of the \xgraph{} in order to build the weak memory model \wmodel{} (Section~\ref{ch:impl:model:wmodel}).
Thereafter, \wmodel{} and transformed \xgraph{} are encoded (Section~\ref{ch:impl:proc:z-encoder}) to a \zformula{} representation (a wrapper over an SMT logical formula), which then is passed as an input to the SMT-solver.

@@

  \item \texttt{YVariableRef} that stores the untyped "reference" to a variable (viz., the name only);

@@

\begin{figure}[t]%[!b]%[H]
  \centering
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/class-diagrams/XEntity-interfaces.png}
  \caption{The inheritance tree of interfaces of \xgraph{}}
  \label{fig:class-diagrams:XEntity-interfaces}
\end{figure}

@@

Following the terminology of the C standard, we distinguish the \textit{r-value} and \textit{l-value} memory units (unlike r-values, the l-values may be assigned a new value).
As r-values cannot change their value, they can be seen as the value itself (therefore the \texttt{XComputationEvent} is modelled as an local r-value memory unit, see more detailed discussion further in current Section).

@@

- memory manager: no contexts so far; locals per process + shareds; register/deregister;

@@

The following interfaces capture main types of events (see also Figure~\ref{fig:class-diagrams:XEntity-interfaces}):

\begin{itemize}
  \item \texttt{XMemoryEvent} \\
  The memory event defines the transfer of the value from one memory unit to another.
  There are four types of memory events (the arrow denotes the direction of the data-flow):
  \begin{enumerate}
  \item \texttt{XRegisterMemoryEvent}: \\
    $\texttt{XLocalLvalueMemoryUnit} \leftarrow \texttt{XLocalMemoryUnit}$
  \item \texttt{XLoadMemoryEvent}: \\
    $\texttt{XLocalLvalueMemoryUnit} \leftarrow \texttt{XSharedMemoryUnit}$
  \item \texttt{XStoreMemoryEvent}: \\
    $\texttt{XSharedLvalueMemoryUnit} \leftarrow \texttt{XLocalMemoryUnit}$
  \item \texttt{XInitialWriteEvent}: \\
    $\texttt{XLvalueMemoryUnit} \leftarrow \texttt{XRvalueMemoryUnit}$

  \end{enumerate}%TODO incompleted enumeration
  %TODO: either say st about getLoc(), getReg(), or remove them from code

  \item \texttt{XComputationEvent} \\
  - binary and unary \\
  - implements both \texttt{XEvent} and \texttt{XMemoryUnit}.
  This is a model-level optimisation possible \textbf{due to} because a computation-event
  %\textit{is} an event (thus it can form a node in \xgraph{}) and it also 
  performs a computation over local-only memory and does not change the value of any memory unit, therefore the \textit{computation} abstraction (the CPU time) can be safely removed from the model, and the computation event can be seen as an atomic operation.

  \item \texttt{XControlFlowEvent} \\
    \texttt{XJumpEvent} no computation, no data operation. may be safely removed for optimisation
    \texttt{XMethodCallEvent} : TODO: meth call should inherit both control-flow and computation.
    itself - computation result (temp register) + if (method resolved) => context binding + jump to the method body

  \item \texttt{XFenceEvent}
    \texttt{XBarrierEvent} : mfence, sync, optsync, lwsync, optlwsync, ish, isb, isync

  \item \texttt{XFakeEvent}
    \begin{enumerate}
    \item \texttt{XEntryEvent}, the source event in the event-flow graph %only event that cannot have incoming edges
    \item \texttt{XExitEvent} : two kinds (depending on the unrolling boundary)
    \item \texttt{XNopEvent} : no-operation event, used for correct encoding (picture); same as simple jump to the next event
    \end{enumerate}

\end{itemize}

Edges (relations edges (just map with enum as kind of edge)):
\begin{enumerate}
\item CF edge: then-edge (primary), else-edge (alternative)
\item DF edge: co, rf
\end{enumerate}

Valid graph:
\begin{enumerate}
\item single source, two sinks
\item connected
\item each node has 1 or 2 children
\item branching node (2 children) instanceof XComputationEvent (evaluation of the value, no shared-memory operations)
\end{enumerate}

consider the following code in C:

picture of the CF-graph:

XEventInfo:
Events are specified by the process generated them and a unique label.
This information is stored by events as the immutable structure \texttt{XEventInfo}.
%hashcode, uniqueness

%\lstinputlisting{inc/XEventVisitor-cleaned.java}

\subsubsection{W-model}
\label{ch:impl:model:wmodel}
%TODO: almost not implemented !
<to be done>

a simple set of recursively defined relations over ..

@@

itemize elements

@@

%todo: after all, list HERE which modules (classes, managers) are being initialised during the pre-compilation. I'ts good to have the dependencies graph on moduls (operational semantics:) )

@@

visitor of antlr tree: almost direct

todo: grammar of w-model to appendix

@@

from ANTLR syntax tree of C

- desugar, equiv transform

- variables distinguished from

@@

- So, The language-dependent syntax tree is converted to the AST by the stateless Visitor (e.g., for C11 -> Ytree conversion is made by 'C2YtreeConverterVisitor') + short structure of this visitor (how?.. need ly?)

@@

%The original program encoded into the \texttt{XGraph} represents a \textit{flow graph}, a connected cyclic directed graph with single source node \texttt{(ENTRY)} (usually for convenience all leaves are connected to the sink node \texttt{(EXIT)}). The cycles are caused by low-level jump instructions, obtained from non-linear high-level control-flow statements (such as \texttt{while}, \texttt{do-while}, \texttt{for}, etc.). However, the cyclic flow graph cannot be encoded into SMT formula since ...
%//TODO:REFERENCE.%TODO

@@

- pointers
- externs
- parameters of process-functions

@@

%TODO: remake this paragraph considering that we have already said sth about XType
The C language has a static (resolved at compile-time) manifest (all types are declared explicitly) type system.
Comparing to languages that use type inference, the type analysis of a C program constitutes a simple propagating the type information (obtained from variables declarations) to all expressions.
%In \porthos[2], the type is modelled by the class \texttt{XType}.%TODO: + fix class and package name!
Being carried at Y and X representation levels, the type is converted to a Z-type at the Z-formula encoding stage (see Section~\ref{ch:impl:proc:z-encoder}).

@@

- X-type construction: code of class YType2TypeConverter (todo: rename: it's not conversion, it's a type construction, from the y-level name+qualifiers+

- The typification algorithm: propagation rules for each of Y

\paragraph{Invocation hooking}
\label{ch:impl:proc:x-pre-compiler:hooks}

resolve the semantics of a function given its signature (meth name + params types)

knowledge base: InterceptionAction(BiFunction<XMemoryUnit, XMemoryUnit[], ? extends XEntity> action)

@@

%MethCallE : bind parameters with values (load them to temp registers) + remember the return-register
%reutrn event= assign the return-register + simple jump

@@

setting up backward edges

how we attempted, why it didn't work in general case:

@@

sth about hashcodes and collections

%TODO: draw (and implement) diff types of exit nodes
\begin{figure}[h]
\centering
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.5cm,semithick]
\node[c] (1) [] {$1$};
\node[c] (2) [below left of=1] {$2$};
\node[c] (3) [below right of=1] {$3$};
\node[c] (4) [below of=3] {$4$};
\path[->]
(1) edge [] node {} (2)
(2) edge [bend left=50,dotted] node {} (1)
(1) edge [] node {} (3)
(3) edge [] node {} (4)
(4) edge [bend right=80,dotted] node {} (1)
;
\node[draw=none] (impl) [right=3cm of 3] {$\overset{k = 6}{\longmapsto}$};
;
\node[c] (21) [right=3cm of impl] {$2_1$};
\node[c] (11) [above right=1cm and 1cm of 21]{$1_1$};
\node[c] (31) [below right=1cm and 1cm of 11] {$3_1$};
\node[c] (41) [below of=31] {$4_1$};
\node[c] (12) [below of=21] {$1_2$};
\node[c] (22) [below left=1cm and 1cm of 12] {$2_2$};
\node[c] (32) [below right=1cm and 1cm of 12] {$3_2$};
\node[c] (13) [below of=41] {$1_3$};
\node[c] (14) [below of=22] {$1_4$};
\node[c] (43) [below of=32] {$4_3$};
\node[c] (23) [below of=13] {$2_3$};
\node[c] (33) [below of=13] {$3_3$};
\node[c] (24) [below left=1cm and 1cm of 14] {$2_4$};
\node[c] (34) [below right=1cm and 1cm of 14] {$3_4$};
\node[c] (15) [below right=1cm and -0.3cm of 43] {$1_5$};
\node[c] (44) [below of=33] {$4_4$};
\node[c] (6) [below left=1cm and 1cm of 15] {$6$};
\node[] (11k) [right=3.2cm of 11] {$(k = 1)$};
\node[] (31k) [right=1.7cm of 31] {$(k = 2)$};
\node[] (41k) [right=1.7cm of 41] {$(k = 3)$};
\node[] (13k) [right=1.7cm of 13] {$(k = 4)$};
\node[] (33k) [right=1.7cm of 33] {$(k = 5)$};
\node[] (44k) [right=1.7cm of 44] {$(k = 6)$};
\path[->]
(11) edge [] node {} (21)
(11) edge [] node {} (31)
(31) edge [] node {} (41)
(21) edge [] node {} (12)
(12) edge [bend right=10] node {} (22)
(12) edge [bend left=10] node {} (32)
(41) edge [] node {} (13)
(22) edge [] node {} (14)
(32) edge [] node {} (43)
(13) edge [] node {} (23)
(13) edge [] node {} (33)
(14) edge [bend right=10] node {} (24)
(14) edge [bend left=10] node {} (34)
(43) edge [] node {} (15)
(33) edge [bend right=10] node {} (15)
(33) edge [bend left=10] node {} (44)
(24) edge [bend right=20] node {} (6)
(34) edge [] node {} (6)
(15) edge [] node {} (6)
(44) edge [bend left=20] node {} (6)
;
\end{tikzpicture}
}
\label{fig:loop-unwind}
\caption{Example of the flow graph from Figure~\ref{fig:merged-loop.....}, unwinded up to the bound $k = 6$}
\end{figure}

@@

- set up co, rf edges => new graph

- computing SSA maps (now: during the encoding. should be: during the post-compilation) (as one of necessary steps before encoding)

@@

Z-type : SMT-specific (say about smt-lib)

@@

<not implemented>

\subsubsection{Logger}
\label{ch:impl:aux:logger}

<not implemented>

@@
